%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%
% Modified by: Zeeshan Hooda
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{amsmath}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[
  left=0.5in,
  right=0.5in,
  top=0.5in,
  bottom=0.5in,
  includefoot,
  footskip=20pt
]{geometry}
\usepackage[us,nodayofweek]{datetime}
%% \renewcommand{\dateseparator}{.}

\input{glyphtounicode}

\newcommand{\deemph}[1]{\small\textit{\color{black!40}#1}}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\fancyfoot[C]{\vfill\deemph{Zeeshan Hooda --- Senior ML Engineer}}
\fancyfoot[R]{\vfill\deemph{Page \thepage~of~\pageref*{LastPage}}}
\fancyfoot[L]{\vfill\deemph{Rev. \today}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%% \addtolength{\oddsidemargin}{-0.5in}
%% \addtolength{\evensidemargin}{-0.5in}
%% \addtolength{\textwidth}{1in}
%% \addtolength{\topmargin}{-.5in}
%% \addtolength{\footskip}{20pt}
%% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
% NOTE: For International Applications
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://zeeshan.hooda.dev/}{\Large Zeeshan Hooda}} & \href{https://zeeshan.hooda.dev/}{zeeshan.hooda.dev}\\
  \href{tel:+15875686239}{+1 (587) 568-6239} & \href{https://linkedin.com/in/zeeshanhooda}{linkedin.com/in/zeeshanhooda} \\
    \href{mailto:zhooda@protonmail.com}{zhooda@protonmail.com} & Canada (Relocating to Australia)
\end{tabular*}

% NOTE: For Local/NA Applications
%% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%%   \textbf{\href{https://zeeshan.hooda.dev/}{\Large Zeeshan Hooda}} & Canadian Citizen\\
%%   \href{tel:+15875686239}{+1 (587) 568-6239} &  \href{https://zeeshan.hooda.dev/}{zeeshan.hooda.dev}\\
%%     \href{mailto:zhooda@protonmail.com}{zhooda@protonmail.com} & \href{https://linkedin.com/in/zeeshanhooda}{linkedin.com/in/zeeshanhooda}
%% \end{tabular*}



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      %% {OpsGuru, A Carbon60 Company}{Toronto, CAN}
      {OpsGuru, A Carbon60 Company}{Toronto, ON}
      {Senior AI/ML Engineer}{Oct 2023 - Present}
      \resumeItemListStart
        \resumeItem{Large Language Models}
          {Reduced qualitative survey analysis times by 95\% for a customer experience management client using DSPy, fine-tuned LLMs on Amazon Bedrock, and classical NLP with spaCy.}
        \resumeItem{Deep Learning}
          {Optimized U-Nets for an energy client, scaling real-time leak detection to 11,800 pipeline miles.}
        \resumeItem{Machine Learning}
          {Operationalized XGBoost promotion targeting system for a toll highway operator, decreasing training times by 30x and saving US\$880K in annual cloud costs.}
        \resumeItem{Machine Learning Operations}
          {Designed and implemented 10+ MLOps solutions on Amazon SageMaker, developing processes, infrastructure, and training materials for each stage in the MLOps workflow.}
      \resumeItemListEnd

% --------Multiple Positions Heading------------
   \resumeSubSubheading
    {Senior Data/ML Engineer}{Oct 2022 - Oct 2023}
    \resumeItemListStart
       \resumeItem{Large Language Models}
         {Engineered a chatbot RAG system for interacting with internal knowledge bases, outperforming Amazon Q by 90\% on question-answering tasks using Amazon Bedrock, Chainlit, and Terraform.}
       \resumeItem{Professional Services}
          {Led cross-functional teams in 20+ Data, ML, and MLOps engagements from pre-sales to completion, including discovery, talent casting, report creation, implementation, and escalations ;-).}
       \resumeItem{Data Modeling}
          {Designed complex canonical data models for public and private sector clients in highly regulated environments, receiving CSAT scores of 9.8+/10.0 for efforts in understanding customer domains.}
    \resumeItemListEnd
   %% \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      %% {Smart Access}{San Francisco, USA}
      {Smart Access}{San Francisco, CA}
      {Lead Data Scientist}{Oct 2021 - Oct 2022}
      \resumeItemListStart
        \resumeItem{Clickstream Analytics}
          {Designed an analytics service to collect 20M+ weekly interactions and enabled high-confidence analysis of multi-event and multi-session clickstreams.}
        \resumeItem{Machine Learning}
          {Reduced seasonal employee turnover for an F500 retailer by 30\% in 70 stores using survival analysis to predict time-to-quit, enabling early intervention and saving US\$4M in annual onboarding costs.}
        %% \resumeItem{Best Practices}
        %%   {Implemented environment isolation for data and analytics infrastructure to alleviate production incidents and adhere to software best practices.}
        %% \resumeItem{Data Warehousing}
        %%   {Setup, schema design and management of Amazon Redshift. Built an internal app for access to the data using a web interface. Dataduct integration for daily ETL injection into Redshift.}
        \resumeItem{Leadership}
          {Staffed and supervised a team of 5 data scientists, engineers, and analysts, balancing ad-hoc analysis requests with long-term goal planning, research and experimentation, and platform maintenance.}
        %% \resumeItem{Content Discovery}
        %%   {Improved content discovery by building a new onboarding experience on coursera. Using this to personalize the search and browse experience. Also worked on ranking and indexing improvements.}
        %% \resumeItem{Course Dashboards}
        %%   {Instructor dashboards and learner surveying tools, which helped instructors run their class better by providing data on Assignments and Learner Activity.}
      \resumeItemListEnd

    \resumeSubSubheading
    {Data Scientist}{Apr 2021 - Oct 2021}
    \resumeItemListStart
       \resumeItem{Natural Language Processing}
         {Improved relevance of search results by 70\% using lemmatization, synonymization, and thematic clustering techniques to enable semantic search of platform content.}
        \resumeItem{Platform Operations}
          {Architected and implemented a self‐serve data and MLOps platform on GCP using BigQuery, Dataproc, Superset, MLFlow, and Python.}
          %% {Architected and implemented a self‐serve data and MLOps platform on GCP using BigQuery, Dataproc, Debezium, Airflow, Superset, MLFlow and Python, increasing data freshness by 20x.}
    \resumeItemListEnd

    \resumeSubheading
      %% {Redman Technologies}{Edmonton, CAN}
      {Global Quantitative Strategies, Citadel}{New York, NY}
      {Visiting Quantitative Researcher, Remote}{Sept 2020 - Apr 2021}
      \resumeItemListStart
        \resumeItem{Machine Learning}
          {Implemented and optimized LightGBM in hardware using SystemVerilog for deployment on Xilinx FPGAs in high-frequency securities trading environments.}
      \resumeItemListEnd


    \resumeSubheading
      %% {SensorUp}{Calgary, CAN}
      {SensorUp}{Calgary, AB}
      {Data Scientist}{Sept 2018 - Sept 2020}
      \resumeItemListStart
        \resumeItem{Computer Vision}
          {Fine-tuned and deployed hazard detection models on edge devices to 400 remote industrial sites using AWS Lambda, DeepStream, and YOLO, reducing average hazard reaction time by 75\%.}
        %% \resumeItem{Data Architecture}
        %%   {Reduced ingestion times of customer data 20x by developing a multi-tenant data platform using Airflow, Python, PySpark, and Redshift.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{ML Delivery Toolkit}
      {Processes and heuristics for evaluating and operationalizing machine learning systems.}
    \resumeSubItem{M2K Classifier}
      {Identifying child-appealing marketing with computer vision and natural language processing.}
    \resumeSubItem{IHL}
      {Research DSL for structured programming of LLM-based applications as a type-safe alternative to DSPy.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      %% {University of California, Berkeley}{Berkeley, USA}
      {University of California, Berkeley}{Berkeley, CA}
      {Doctor of Philosophy in Computer Science (In Progress)\vspace{4pt}}{Sparsity in Clickstream Inference}
    %% \resumeSubSubheading
    %%   {Master of Science (MSc) in Computer Science\vspace{4pt}}{2023}
    \resumeSubSubheading
      {Bachelor of Science in Computer Science and Statistics (summa cum laude)}{Statistical Machine Learning}
      %% {Bachelor of Science (BSc) in Computer Science;  GPA: 3.98/4.00}{Sept 2019 -- Apr 2022}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Languages}{Python, SQL, Go, C, Scala, JavaScript, OCaml, ReasonML, CUDA, MLIR, SystemVerilog, \LaTeX}
   \resumeSubItem{Technologies}{AWS, GCP, Terraform, Docker, Kafka, Trino, Spark/MLlib PyTorch, JAX/XLA, scikit-learn, spaCy}
 \resumeSubHeadingListEnd


\section{Manuscripts in Review}
  \resumeSubHeadingListStart
    \resumeSubItem{MarkovEFB}
      {Improving sparse clickstream gradient boosting with Markov-modulated exclusive feature bundling.}
    \resumeSubItem{LegalCoder}
      %% {LLM-based annotator for legal texts to produce verifiable code implementations in the Catala DSL.}
      %% {Automating formal verification of legislative texts with LLM-based annotation of Catala code.}
      {Automating formal verification of legislative texts using language model annotators for the Catala DSL.}
    \resumeSubItem{InaraNet}
      {Antimicrobial peptide recognition with involutional and long short-term memory neural networks.}
    %% \resumeSubItem{MarkovGBM}
    %%   {Markov-modulated feature bundling for efficient gradient boosting on sparse clickstreams.}
  \resumeSubHeadingListEnd

\section{Awards and Grants}
 \resumeSubHeadingListStart
   \resumeSubItem{Citadel GQS Fellowship}{One-year PhD fellowship providing US\$100,000 in research funding ($2\times$).}
   \resumeSubItem{NSERC PGS Doctoral}{Three-year PhD scholarship providing CA\$63,000 in research funding ($1\times$).}
   \resumeSubItem{Fulbright Canada Student}{One-year undergraduate grant providing US\$25,000 in funding ($3\times$).}
   %% \resumeSubItem{Apple Scholars in AI/ML}{Two-year PhD fellowship providing mentorship and US\$90,000 in funding.}
 \resumeSubHeadingListEnd

%-------ADDITIONAL EXPERIENCE----------
\section{Previous Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      %% {Sprout Fund}{Edmonton, CAN}
      {Sprout Fund I/II}{Edmonton, AB}
      {Venture Capital Advisor, AI/ML}{Sept 2020 - Present}
      \resumeItemListStart
        \resumeItem{Investment Analysis}
          {Evaluated 40+ ML-focused startup companies for technical viability and product-market fit, providing decision support and knowledge translation to the investment management team.}
      \resumeItemListEnd

    \resumeSubheading
      %% {Redman Technologies}{Edmonton, CAN}
      {Redman Technologies}{Edmonton, AB}
      {Software Engineer (Internship)}{Summer 2017, 2018}
      \resumeItemListStart
        \resumeItem{Full-stack}
          {Built a visualization platform for neighborhood statistics using CouchDB, Node.js, and Express deployed to 1400+ Realtors across Canada.}
      \resumeItemListEnd

    \resumeSubheading
      {Mozilla Foundation}{Portland, OR}
      %% {Compiler Engineer Intern}{Portland, USA}
      {Compiler Engineer (Internship)}{Summer 2016}
      \resumeItemListStart
        \resumeItem{Memory Allocation}
          {Designed and implemented a type-partitioning memory allocator used in experimental browser engines, scripting language runtimes, and just-in-time compilers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% ------- QUOTE -------
%% \hrule
%% \vspace*{\fill}
%% \begin{center}
%%   \parbox{90mm}
%%          {\textit{Your scientists were so preoccupied with whether they could, they didn’t stop to think if they should.} \\
%%           \vspace{-1.5em}
%%           \begin{flushright}
%%             ---\textit{Jurrasic Park (1993)}
%%           \end{flushright}
%%           }
%% \end{center}
%% \vspace*{\fill}

%-------------------------------------------
\end{document}
